A finite-state morphological transducer for Kyrgyz

### 2011-10-17 dev/paper/paper.tex
update ambig scores
arabic font rendering issues fixed

@@

\section{Background}
Kyrgyz (written ‹кыргыз тили› or ‹قىرعىر تىلى›, pronounced [qɯɾʁɯz tili]) alternatively written ``Kirghiz'' or ``Kirgiz'') is a Turkic language spoken in Kyrgyzstan, China, Tajikistan, and Uzbekistan.  Its classification within Turkic remains problematic—it appears to alternatively belong to the Kypchak (Northwestern) branch and to the South Siberian (Northeastern) branch.  The Turkic varieties phonetically and phonologically most similar to Kyrgyz are the southern dialects of Altay, though Kyrgyz shows strong parallels to Kazakh that these varieties lack, especially in its Talas dialects.  In southern varieties of Kyrgyz there are also many similarities to Uzbek that other dialects lack.

@@

\begin{table}
	\centering
	\begin{tabular}{lrrrr}
		\toprule
		Corpus           & Tokens    & Known     & Naïve coverage    & Mean ambiguity\\
		\midrule
		Kyrgyz Wikipedia & 329,524   & 269,573   & 81.84 $\pm$ 3.23  & 4.53\\
		RFERL Kyrgyzstan & 4,107,555 & 3,586,000 & 87.37 $\pm$ 1.23  & 4.26\\
		\bottomrule
	\end{tabular}
	\caption{FIXME}
	\label{table:cov}
\end{table}

>>>>

\usepackage[novoc,fdf2alif]{arabxetex}
\newfontfamily\uighurfont[Script=Arabic,Scale=1.5]{Lateef}

@@

\section{Background}
Kyrgyz (written ‹кыргыз тили› or ‹\textuighur{قىرعىز تىلى}›, pronounced [qɯɾʁɯz tili]) alternatively written ``Kirghiz'' or ``Kirgiz'') is a Turkic language spoken in Kyrgyzstan, China, Tajikistan, and Uzbekistan.  Its classification within Turkic remains problematic—it appears to alternatively belong to the Kypchak (Northwestern) branch and to the South Siberian (Northeastern) branch.  The Turkic varieties phonetically and phonologically most similar to Kyrgyz are the southern dialects of Altay, though Kyrgyz shows strong parallels to Kazakh that these varieties lack, especially in its Talas dialects.  In southern varieties of Kyrgyz there are also many similarities to Uzbek that other dialects lack.

@@

\begin{table}
	\centering
	\begin{tabular}{lrrrr}
		\toprule
		Corpus           & Tokens    & Known     & Naïve coverage    & Mean ambiguity\\
		\midrule
		Kyrgyz Wikipedia & 329,524   & 269,573   & 81.84 $\pm$ 3.23  & 4.54\\
		RFERL Kyrgyzstan & 4,107,555 & 3,586,000 & 87.37 $\pm$ 1.23  & 4.46\\
		\bottomrule
	\end{tabular}
	\caption{FIXME}
	\label{table:cov}
\end{table}
